A saturation model for impaired learning with enhanced plasticity: Supplementary material

### 2013-04-30 MHCpaper/MHCsupp.tex
clean up

We will assume $f\dep\wt=f\dep\ko$.
This is because the effects of the mutation is well localised to the Purkinje cells, so the activity of the parallel and climbing fibres should not change very much.
Therefore the rates of potentiation and depression should not change very much either.
This implies that the mean synaptic weight in equilibrium differs between the mutant and wild type, but that is also suggested by the data regarding basal levels of phospho-GluR2 at serine 880.
As the mutation produces no change in baseline performance, there must be a compensatory mechanism somewhere else.
We will model this compensation as a simple linear offset, as could be produced by another population of neurons/synapses whose effect cancels with these neurons/synapses.

@@

Now, consider the mutant, for which we define $\beta=q\pot/q\dep<1$, and we set $q\pot=q$.
Without pre-training:
%
\begin{equation}\label{eq:binKOnopre}
  \Phi = \frac{2{\Delta f}\, q}{1+\beta},
\end{equation}
%
which is always larger that \eqref{eq:binWTnopre}, unlike what is seen in the experiment.
This is also seen in \autoref{fig:binary}\ref{fig:binary_learn},\ref{fig:binary_learnS} (solid curves).
As discussed above (below \eqref{eq:multiKOnopre}), the larger value of $q\dep=q/\beta$ has two effects.
Smaller $\beta$ will increase the probability of depression, speeding up learning, but it will also decrease the probability of being ready for depression, slowing down learning.
For the step-multistate model, we argued that the first effect goes like $1/\beta$, whereas the second goes like $\beta^{M/2}$ to leading order.
Here $M=2$, so the leading part of the two effects will cancel.
The subleading effects are responsible for the faster learning in the mutant.

>>>>

We will assume $f\dep\wt=f\dep\ko$.
This is because the effects of the mutation are well localised to the Purkinje cells, so the activity of the parallel and climbing fibres should not change very much.
Therefore the rates of potentiation and depression should not change very much either.
This implies that the mean synaptic weight in equilibrium differs between the mutant and wild type, but that is also suggested by the data regarding basal levels of phospho-GluR2 at serine 880.
As the mutation produces no change in baseline performance, there must be a compensatory mechanism somewhere else.
We will model this compensation as a simple linear offset, as could be produced by another population of neurons/synapses whose effect cancels with these neurons/synapses.

@@

Now, consider the mutant, for which we define $\beta=q\pot/q\dep<1$, and we set $q\pot=q$.
Without pre-training:
%
\begin{equation}\label{eq:binKOnopre}
  \Phi = \frac{2{\Delta f}\, q}{1+\beta},
\end{equation}
%
which is always larger that \eqref{eq:binWTnopre}, unlike what is seen in the experiment.
This is also seen in \autoref{fig:binary}\ref{fig:binary_learn},\ref{fig:binary_learnS} (solid curves).
As discussed above (below \eqref{eq:multiKOnopre}), the larger value of $q\dep=q/\beta$ has two effects.
Smaller $\beta$ will increase the probability of depression, speeding up learning, but it will also decrease the probability of being ready for depression, slowing down learning.
For the step-multistate model, we argued that the first effect goes like $1/\beta$, whereas the second goes like $\beta^{M/2}$ to leading order.
Here $M=2$, so the leading part of the two effects will cancel.
The subleading effects (the normalisation of the probabilities) are responsible for the faster learning in the mutant.
